TBD

### 2019-02-06 inverse_problems/inverse_problems.tex
updates

The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
We consider the following observation model. Let $X =\RL$ be a random vector drawn from some fixed distribution.
In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

@@

\begin{proposition} \label{prop:poisson}
	The first moment of the Poisson process is equal to:
	%
	\begin{align}
	\gamma \L_1.
	\end{align}
	%
	The second moment vector of the Poisson process has entries
	%
	\begin{align}
	(\gamma \L_1)^2 + \gamma \L_2(\Delta),
	\end{align}
	%
	for $0 \le \Delta < L$.

	The third moment matrix of the Poisson process has entries
	\begin{align}
	(\gamma \L_1)^3 + \gamma \L_1  \cdot ( \gamma\L_2(\Delta_1) + \gamma\L_2(\Delta_2) + \gamma\L_2(\Delta_2-\Delta_1)) + \gamma \L_3(\Delta_1,\Delta_2) ,
	\end{align}
	for $0 \le \Delta_1,\Delta_2 < L$.
\end{proposition}

>>>>

The models we described so far assume a well-separated support. The separation condition can be alleviated by assuming a Poisson process. 
We consider the following observation model. Let $X \in\RL$ be a random vector drawn from some fixed distribution.
In this model, points are chosen in $\{1,\dots,N-L+1\}$ according to a Poisson process with parameter $\gamma N$. The parameter $\gamma$ can be thought of as the density of the $X$ in $Y$.
For each point $i$ that is chosen from $1$ to $N-L+1$, a random vector $X$ from the distribution is then placed in the large vector, with element $0$ at location $i$, with overlapping vectors being added together.

@@

\begin{proposition} \label{prop:poisson}
    For each $i=0,\ldots,L-1$,  the moments of the Poisson process are equal to 
    \begin{align}
    m_Y^1[i] &= \gamma a_X^1 \nonumber \\
    m_Y^2[i,i+\ell] &= (\gamma a_X^1)^2 + \gamma a_X^2[\ell],\quad \ell=0,\ldots,L-1, \\
    m_Y^3[i,i+\ell_1,i+\ell_2] &= (\gamma a_X^1)^3 + \gamma a_X^1  \cdot ( \gamma a_X^2[\ell_1] + \gamma a_X^2[\ell_2] + \gamma a_X^2[\ell_2-\ell_1]) + \gamma a_X^3[\ell_1,\ell_2]. \nonumber  
    \end{align}
\end{proposition}
